MLH1 data report 

### 2017-09-21 rmd_report.rmd
knitd Rmd report

bb <- ggplot(data = dat, aes(x=samplesize, y=MLH1_sample)) + geom_boxplot(aes(fill=samplesize))

```
#omg finally that took so long. main interpertations: the variance grows with larger sample size.
#these are representations of independant samples -- I need to think of a way to show an average of the stats for multiple simulations.

@@

v <- ggplot(data = datf, aes(x=samplesize, y=MLH1_sample)) + geom_boxplot(aes(fill=samplesize) ) 
v                                                                         
v + ggtitle("varying sample sizes") 
```
Can the above code be repeated for a larger number of mice (both passing and non-passing) to show the different effects across samples sizes?
power calculations.... from a preivous document --- I showed myself that for 15 (good) cells, would provide a sample big enough to detect a difference of 3 foci. I only did this for a couple mice, I'll try to re-code for every mouse

@@

#make a column to mark if observation comes from passed or not passed mouse
#turn this into boxplot and sort the category order, otherwise it's hard to any patterns
sc <- qplot(mouse, nMLH1.foci,  colour = category, data = non_passed_mice_data, main="s", xlab="s", ylab="es")
sc + theme(legend.position="none")

sc <- qplot(mouse, nMLH1.foci,  colour = category, data = passed_mice_data, main="s", xlab="s", ylab="es")
sc + theme(legend.position="none")

@@

pwr5mice <- pwr.norm.test(d = (3/sd.count), n = 20, sig.level = 0.05, alternative = "two")$power
data.frame(Nmice=Nmice, cv.count = cv, ttest=ttest, CIlower = ttestCI.lowr, 
           CIupr = ttestCI.upr,
 pwr = pwr5mice, ttest.est=ttest.est)
})
category_pwr_stat
```

```{r}
plot(category_pwr_stat$category, category_pwr_stat$ttest.est)
```
I am not sure how to interpert these power calqs. The estimates are all overlapping.. I guess I shouldn't be suprised by this?

>>>>

bb <- ggplot(data = dat, aes(x=samplesize, y=MLH1_sample)) + #geom_boxplot(aes(fill=samplesize))

@@

v <- ggplot(data = datf, aes(x=samplesize, y=MLH1_sample)) + geom_boxplot(aes(fill=samplesize) ) 
#v                                                                         
#v + ggtitle("varying sample sizes") 
```
Can the above code be repeated for a larger number of mice (both passing and non-passing) to show the different effects across samples sizes?
power calculations.... from a preivous document --- I showed myself that for 15 (good) cells, would provide a sample big enough to detect a difference of 3 foci. I only did this for a couple mice, I'll try to re-code for every mouse

@@

#make a column to mark if observation comes from passed or not passed mouse
#turn this into boxplot and sort the category order, otherwise it's hard to any patterns
sc <- qplot(mouse, nMLH1.foci,  colour = category, data = non_passed_mice_data, main="s", xlab="s", ylab="es")
#sc + theme(legend.position="none")

sc <- qplot(mouse, nMLH1.foci,  colour = category, data = passed_mice_data, main="s", xlab="s", ylab="es")
#sc + theme(legend.position="none")

@@

pwr5mice <- pwr.norm.test(d = (3/sd.count), n = 20, sig.level = 0.05, alternative = "two")$power
data.frame(Nmice=Nmice, cv.count = cv, ttest=ttest, CIlower = ttestCI.lowr, 
           CIupr = ttestCI.upr,
 pwr = pwr5mice, ttest.est=ttest.est)
})
#category_pwr_stat
```

I am not sure how to interpert these power calqs. The estimates are all overlapping.. I guess I shouldn't be suprised by this?
